Estimating Gaze Duration Error from Eye Tracking Data

### 2023-03-24 acm_version/paper.tex
Paper update for conference

\begin{equation}
\label{eq:p_of_d}
P(d|\hat{d},l,s) =  \frac{ P(\hat{d},l,s|d) \dot P(d) }{ P(\hat{d},l,s)  }
\end{equation}

We use a uniform prior for $P(d)$, meaning in the absence of additional information all
gaze durations less than the session length are equally likely. As our distributions are
discrete estimations of an underlying continuous distribution the value of $P(d)$ is
equal to $1/(1+floor(i*s))$. We can estimate the value
of the denominator $P(\hat{d},l,s)$ by iterating over all values of $d$ and summing the product
of $ P(\hat{d},l,s|d) \dot P(d)$. This fully explicated form is shown in 
Equation \ref{eq:p_of_d_full}.

\begin{equation}
\label{eq:p_of_d_full}
P(d|\hat{d},l,s) =  \frac{ P(\hat{d},l,s|d) \dot P(d) }{ \sum_{\delta \in D} P(\hat{d},l,s|\delta) \dot P(\delta)  }
\end{equation}

@@

\begin{figure*}[h!]
\includegraphics[scale=0.5]{../results/Measured_vs_expected.png}
\caption{Measured Gaze Duration Versus Expected Gaze Duration. \\\hspace{\textwidth} 
MREC ad appearing on screen for 1s with 70px Mean Error in Fixation}
\label{fig:measured_vs_expected}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.4]{../results/Fixation_vs_duration_error.png}
\caption{Fixation error versus gaze duration error.}
\label{fig:fixation_vs_duration}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.4]{../results/Error_surface.png}
\caption{Mean gaze duration error over measured error and fixation MAE.}
\label{fig:error_surface}
\end{figure*}

>>>>

\begin{equation}
\label{eq:p_of_d}
P(d|\hat{d},l,s) =  \frac{ P(\hat{d}|l,s,d) P(d|l,s) }{ P(\hat{d}|l,s)  }
\end{equation}

We use a uniform prior for $P(d|l,s)$, meaning in the absence of additional information all
gaze durations less than the session length are equally likely. As our distributions are
discrete estimations of an underlying continuous distribution the value of each discrete
value in $P(d|l,s)$ is
equal to $1/(1+floor(s/i))$. We can estimate the value
of the denominator $P(\hat{d}|l,s)$ by iterating over all possible values of $\delta \in D$ 
and summing the product of $P(\hat{d}|l,s,\delta)$ and $P(\delta|l,s)$. 
This fully explicated form is shown in Equation \ref{eq:p_of_d_full}.

\begin{equation}
\label{eq:p_of_d_full}
P(d|\hat{d},l,s) =  \frac{ P(\hat{d}|l,s,d) P(d|l,s) }{ \sum_{\delta \in D} P(\hat{d}|l,s,\delta) P(\delta|l,s) }
\end{equation}

@@

\begin{figure*}[h!]
\includegraphics[scale=0.5]{results/Measured_vs_expected.png}
\caption{Measured Gaze Duration Versus Expected Gaze Duration. \\\hspace{\textwidth} 
MREC ad appearing on screen for 1s with 70px Mean Error in Fixation}
\label{fig:measured_vs_expected}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.4]{results/Fixation_vs_duration_error.png}
\caption{Fixation error versus gaze duration error.}
\label{fig:fixation_vs_duration}
\end{figure*}

@@

\begin{figure*}[h!]
\centering
\includegraphics[scale=0.4]{results/Error_surface.png}
\caption{Mean gaze duration error over measured error and fixation MAE.}
\label{fig:error_surface}
\end{figure*}
